Open-source landscape for 3D CSEM modelling

### 2020-10-02 manuscript/Manuscript.tex
Updates from Overleaf

\begin{enumerate}
  \item The error levels are overall comparable; the NRMSD is generally below a few percent, increasing towards larger offsets.
  \item The NRMSD between the FV codes \emg3d and \simpeg is very low except at the boundary. The generally very low NRMSD is because these codes use the same rectilinear mesh for modelling. The increasing NRMSD towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition.
  \item The FE codes \custem and petgem show similar boundary effects, but are influenced by the anomaly response (higher errors on right side and now unsymmetrical error distribution).
\end{enumerate}

@@

\imycom[RR]{Is it possible to force a placement of the tables in the corresponding section? (every table is shifted to the next section, quite unituitive to correlate to the models)}

@@

The responses for all six frequencies, both inline and broadside, for all three electric components are shown in Figure~\ref{fig:results-marlim-responses}. The published responses are shown in color (and with markers), and the responses from our codes are shown beneath in grey colours in this overview plot.
%
\plot*{results-marlim-responses}{width=\textwidth}{MR3D comparison between our codes (grey lines) and the published data (coloured lines). The grey lines under the coloured lines are not visible in most areas, meaning they are very similar. However, there are three notable zones, (1) to (3), which are explained further in the text.}
%
Two datasets were published, one containing clean responses, and one where realistic noise was added. For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m. It can be seen that the grey lines are not visible for most parts, which means that the data agree very well. However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.

\imycom[RR]{I'd state point 1 at last (most obvious and least important in my opinion)}
\begin{enumerate}
  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all. In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here come from 3D effects, but they are very low, roughly two orders of magnitude lower than the $E_x$ component. The published responses are not stable either, and therefore any of the responses is as bad as the other. Also, tiniest differences in meshing will have a huge effect here.
  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level). The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components. The differences are related to the bathymetry. And the reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally. See the discussion around Figure~\ref{fig:results-marlim_survey}.
\end{enumerate}

>>>>

\begin{enumerate}
  \item The error levels are overall comparable; the NRMSD is generally below a few percent, increasing towards larger offsets.
  \item The NRMSD between the FV codes \emg3d and \simpeg is comparably low except at the boundary. The generally low NRMSD is because these codes use the same rectilinear mesh for modelling. The increasing NRMSD towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition.
  \item The FE codes \custem and \petgem show similar boundary effects, but are influenced by the anomaly response (higher errors on right side and now unsymmetrical error distribution).
  \item The agreement within the same differential equation method (FE or FV) is better than across methods. 
\end{enumerate}

@@

@@

The responses for all six frequencies, both inline and broadside, for all three electric components are shown in Figure~\ref{fig:results-marlim-responses}. The published responses are shown in color (and with markers), and the responses from our codes are shown beneath in grey colours in this overview plot.
%
\plot*{results-marlim-responses}{width=\textwidth}{MR3D comparison between our codes (grey lines) and the published data (coloured lines). The grey lines under the coloured lines are not visible in most areas, meaning they are very similar. However, there are three notable zones, (1) to (3), which are explained further in the text.}
%
Two datasets were published, one containing clean responses, and one where realistic noise was added. For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m. It can be seen that the grey lines are not visible for most parts, which means that the data agree very well. However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.
\begin{enumerate}
  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level). The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components. The differences are related to the bathymetry. And the reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally. See the discussion around Figure~\ref{fig:results-marlim_survey}.
  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all. In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here come from 3D effects, but they are very low, roughly two orders of magnitude lower than the $E_x$ component. The published responses are not stable either, and therefore any of the responses is as bad as the other. Also, tiniest differences in meshing will have a huge effect here.
\end{enumerate}
